Supplement to Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-02-22 supplement.tex
I added the old IDl mie scattering model and amplitude fits.

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/mie_fits/amp_vs_wavl_j1821_mie_sc.pdf}
\caption{Amplitude spectrum using the \texttt{IDL} fits and holding the rotational period fixed at the literature value.
Representative Mie-scattering models are shown for a particle size distribution of 0.1$\mu$m and 0.2$\mu$m pyroxene grains.}\label{fig:IDLmieScatterA1821}
\end{centering}
\end{figure}
